Spatiotemporal transmission risk

### 2023-04-20 analysis/spatiotemporal-transmission-risk.Rmd
preparing and testing spatiotemporal model with diffusion

# plot with and height of input and data graphs
width_descr <- 10.5 / cm(1)
height_descr <- 7.5 / cm(1)
text_descr <- 12
```

@@

# for abstract
highRiskPat_pl_abs <- highRiskPat_pl +
  labs(title = "1a | Estimated no. of attendees with high-risk of MtB infection",
       subtitle = "Number (mean and 95%-limits) of high-risk clinical attendees (defined as P>1%)") +
  theme(plot.title = element_text(face = 2),
        plot.title.position = "plot")

summary_tab_abs <- summary_tab +
  labs(title = " ",
       subtitle = " ")

qc_pl_abs <- qc_pl +
  labs(title = "1b | Estimated quanta concentration in the clinic by daytime",
        subtitle = "Average concentration in the morning (7:30 to 12am) and afternoon (12am to 4pm)") +
  theme(plot.title = element_text(face = 2))

comb_abs_pl <- grid.arrange(grid.arrange(highRiskPat_pl_abs, summary_tab_abs, ncol = 2, widths = 16 * c(0.7,.3)), qc_pl_abs, ncol = 1, heights = 25 / cm(1) * c(0.35, 0.65))
ggsave(plot = comb_abs_pl, filename = "../doc/Union/abstract/figure.png", width = 16 / cm(1), height = 25 / cm(1))
```

>>>>

# plot with and height of input and data graphs
width_descr <- 10.5 / cm(1)
height_descr <- 7.5 / cm(1)
text_descr <- 10
```

@@

# for abstract
# highRiskPat_pl_abs <- highRiskPat_pl +
#   labs(title = "1a | Estimated no. of attendees with high-risk of MtB infection",
#        subtitle = "Number (mean and 95%-limits) of high-risk clinical attendees (defined as P>1%)") +
#   theme(plot.title = element_text(face = 2),
#         plot.title.position = "plot")
# 
# summary_tab_abs <- summary_tab +
#   labs(title = " ",
#        subtitle = " ")

qc_pl_abs <- qc_pl +
  labs(title = "1b | Estimated quanta concentration in the clinic by daytime",
        subtitle = "Average concentration in the morning (7:30 to 12am) and afternoon (12am to 4pm)") +
  theme(plot.title = element_text(face = 2))
```

x### Track examples

```{r}
examples <- no_people %>%
  group_by(patient_id) %>%
  mutate(first_entered = first(is_entrance),
         last_exited = last(is_entrance|is_exit),
         duration = as.numeric(difftime(last(time), first(time), units = "mins"))) %>%
  ungroup() %>%
  filter(first_entered,
         last_exited,
         duration > 10) %>%
  ungroup()

n_distinct(examples$patient_id)

examples_se <- examples %>%
  group_by(patient_id) %>%
  slice(1, n()) %>%
  mutate(type = factor(c("Start", "End"), levels=c("Start", "End"))) %>%
  ungroup()

examples_pl <- examples %>%
  ggplot(aes(x = x, y = y, group = patient_id)) +
  geom_path(color = "darkred", alpha = .5) +
  geom_point(data = examples_se, mapping = aes(shape = type)) +
  ggpubr::background_image(clinic_img) +
  scale_y_continuous(expand = expansion(add=c(2000, 3250))) +
  scale_x_continuous(expand = expansion(add=c(800, 0))) +
  scale_shape_manual(values = c(1,13)) +
  annotation_custom(entrance_lab, xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf) +
  annotation_custom(wr_lab, xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf) +
  annotation_custom(tb_lab, xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf) +
  annotation_custom(re_lab, xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf) +
  labs(title = "1a | Subset of patient movement data",
       subtitle = "Examples of trackings from 40 patients in the clinic") + 
  theme_classic() +
  theme(text = element_text(size = text_descr),
        axis.text = element_blank(), axis.title = element_blank(), axis.ticks = element_blank(), legend.key.width = unit(0.3, "cm"), legend.key.height = unit(0.3, "cm"),
        legend.position = c(0.825,0.075), legend.direction = "horizontal",
        panel.background = element_rect(fill = RColorBrewer::brewer.pal(n = 9, name = "YlOrRd")[1]), panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), legend.title = element_blank()) +
  theme(plot.title = element_text(face = 2))

examples_pl

comb_abs_pl <- grid.arrange(grid.arrange(examples_pl, ggplot() + theme_classic() + theme(axis.line = element_blank()), ncol = 1, heights = c(8.5,6.5)), 
                            qc_pl_abs, ncol = 2, widths = 26.5 / cm(1) * c(0.475, 0.525))
ggsave(plot = comb_abs_pl, filename = "../doc/Union/abstract/figure.png", width = 26.5 / cm(1), height = 15 / cm(1))
```
